### 2014-08-14 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: minor update to report, update devices in input files

\begin{tabbing}
\hspace{1.5in} \= \\
EMS \> Emergency Medical Services \\
FDS \> Fire Dynamics Simulator \\
HGL \> Hot Gas Layer \\
HRR \> Heat Release Rate \\
HRRPUA \> Heat Release Rate per Unit Area \\
LODD \> Line of Duty Death \\
NIST \> National Institute of Standards and Technology \\
SFPE \> Society of Fire Protection Engineers \\
\end{tabbing}

@@

On February 24, 2012, a fire in residential structure injured seven Prince George's County firefighters. NIST examined the fire dynamics of this incident at the request of the Prince George's Country Fire/Emergency Medical Services (EMS) Department. Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide}  software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire. The specific objectives of the simulations detailed in this report are: 
\begin{enumerate}
\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this multi-story residential structure using physics-based calculations.
\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Prince George's Fire Department likely experienced during the course of their interior operations.
\end{enumerate}
This document describes the input and the results of the FDS (version 6.0.0) simulations. The simulations were developed using a combination of knowledge of the fire scenario and appropriate engineering approximations and assumptions. Analysis of the simulation results focuses on the hazardous conditions that developed following the development of a flow path inside of the structure. This document is organized as follows: Section~\ref{fire_sum} provides a summary of the fire incident, Section~\ref{model} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{results} presents the simulation results, and Section~\ref{discuss} discusses the simulation results as they relate to firefighter safety and effectiveness. Appendix~\ref{app_draw} contains dimensioned drawings of the first and second floor of the structure.

@@

\noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events.
\begin{table}[!h]
\centering
\captionof{table}[Abridged approximate fire event timeline]{Abridged Prince George's Fire/EMS approximate fire event timeline~\cite{PGCounty2013}}\label{tab:fire_info}
\begin{tabular}{cl}
\toprule[1.5pt]
Incident Time              &  Fire Behavior / Fireground Operation  \\
{[hh:mm:ss]}               &                                                               \\
\midrule
21:08:26   & First 911 call is made. \\[.25cm]
\multirow{3}{*}{21:11:03}  &   \multirow{3}{*}{\parbox{10cm} {Dispatch for a ``box'' alarm assignment- four engine companies, two truck companies, one rescue squad, and a commanding officer.}}    \\
                           &         \\
                           &         \\[.25cm]
21:12:55  &  First unit (Engine 807B) arrived on-scene.  \\[.25cm]
21:13:44  & Volunteer Chief 809A establishes incident command (IC).   \\[.25cm]
21:13:56  & Truck 809 arrived on-scene. \\[.25cm]
21:14:00  & Front door opened. \\[.25cm]
21:14:42  & Truck 809 enters structure. \\[.25cm]
21:15:47  & Front door closed over. \\[.25cm]
21:15:51  & Lower pane of front egress window broke. \\[.25cm]
21:15:57  & Water applied to fire at basement. \\[.25cm]
21:16:01  & Top pane of front egress window broke. \\[.25cm]
21:16:16  & Truck 809 officer bailout through window. \\[.25cm]
21:16:44  & Front door opened. \\[.25cm]
21:17:15  & Truck 809 forcible entry firefighter rescued. \\[.25cm]
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

>>>>

\begin{tabbing}
\hspace{1.5in} \= \\
EMS \> Emergency Medical Services \\
FDS \> Fire Dynamics Simulator \\
HGL \> Hot Gas Layer \\
HRR \> Heat Release Rate \\
HRRPUA \> Heat Release Rate per Unit Area \\
LODD \> Line of Duty Death \\
NIST \> National Institute of Standards and Technology \\
PPE \> Personal Protective Equipment \\
SCBA \> Self Contained Breathing Apparatus \\
SFPE \> Society of Fire Protection Engineers \\
\end{tabbing}

@@

On February 24, 2012, a fire in residential structure injured seven Prince George's County firefighters. NIST examined the fire dynamics of this incident at the request of the Prince George's Country Fire/Emergency Medical Services (EMS) Department. Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide}  software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire. The specific objectives of the simulations detailed in this report are: 
\begin{enumerate}
\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this multi-story residential structure using physics-based calculations.
\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Prince George's Fire Department likely experienced during the course of their interior operations.
\end{enumerate}
This document describes the input and the results of the FDS (version 6.1.1) simulations. The simulations were developed using a combination of knowledge of the fire scenario and appropriate engineering approximations and assumptions. Analysis of the simulation results focuses on the hazardous conditions that developed following the development of a flow path inside of the structure. This document is organized as follows: Section~\ref{fire_sum} provides a summary of the fire incident, Section~\ref{model} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{results} presents the simulation results, and Section~\ref{discuss} discusses the simulation results as they relate to firefighter safety and effectiveness. Appendix~\ref{app_draw} contains dimensioned drawings of the basement and first floor of the structure.

@@

The Prince George's County report~\cite{PGCounty2013}  \noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events.
\begin{table}[!h]
\centering
\captionof{table}[Abridged approximate fire event timeline]{Abridged Prince George's Fire/EMS approximate fire event timeline~\cite{PGCounty2013}}\label{tab:fire_info}
\begin{tabular}{cl}
\toprule[1.5pt]
Incident Time              &  Fire Behavior / Fireground Operation  \\
{[hh:mm:ss]}               &                                                               \\
\midrule
21:08:26   & First 911 call is made. \\[.25cm]
\multirow{3}{*}{21:11:03}  &   \multirow{3}{*}{\parbox{10cm} {Dispatch for a ``box'' alarm assignment- four engine companies, two truck companies, one rescue squad, and a commanding officer.}}    \\
                           &         \\
                           &         \\[.25cm]
21:12:55  &  First unit (Engine 807B) arrived on-scene.  \\[.25cm]
21:13:44  & Volunteer Chief 809A establishes incident command (IC).   \\[.25cm]
21:13:56  & Truck 809 arrived on-scene. \\[.25cm]
21:14:00  & Front door opened. \\[.25cm]
21:14:42  & Truck 809 enters structure. \\[.25cm]
21:15:47  & Front door closed over. \\[.25cm]
21:15:51  & Lower pane of front egress window broke. \\[.25cm]
21:15:57  & Water applied to fire at basement. \\[.25cm]
21:16:01  & Top pane of front egress window broke. \\[.25cm]
21:16:16  & Truck 809 officer bailout through window. \\[.25cm]
21:16:44  & Front door opened. \\[.25cm]
21:17:15  & Truck 809 forcible entry firefighter rescued. \\[.25cm]
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}
